---
title: "Alaskan Catch of BC Salmon"
output: html
execute:
  echo: false
  message: false
  warning: false
---

```{r}
library(data.table)
library(tidyverse)

```

## Skeena

### Sockeye

Information on Alaskan exploitation of Skeena sockeye comes primarily from the Northern Boundary Sockeye Run Reconstruction model, which uses estimated run-timing and migration route to provide estimates of interception rates in Alaska fisheries. We show timeseries of Alaskan exploitation rates for each Skeena sockeye Conservation Unit with information (@fig-skeena-trtc1) and the distribution of exploitation rates (@fig-skeena-trtc2).

```{r, fig.height=10,fig.cap="Alaskan exploitation rates for each Skeena sockeye Conservation Unit (1960-2023)."}
#| label: fig-skeena-trtc1

data<-fread("data-raw/sockeye-skeena-trtc data.csv")

data$`AK ER`<-data$`Total ER`-data$`CDN ER`

#line plot of ak ers for each skeena cu
ggplot(data,aes(x=Year,y=`AK ER`))+
  geom_point()+geom_line()+
  facet_wrap(CU_Name~.,ncol=3)+
  labs(y="Alaskan Exploitation Rate")+
  theme_bw()
```

```{r,fig.height=8,fig.cap="Distribution of Alaskan exploitation rates on each Skeena sockeye CU with information (1960-2023)."}
#| label: fig-skeena-trtc2

#boxplot of ak ers for each skeena cu
ggplot(data,aes(x=`AK ER`,y=reorder(CU_Name,`AK ER`,median),fill=CU_Name))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(height=.1)+
  labs(y="Conservation Unit",x="Alaskan Exploitation Rate")+
  theme_bw()+
  guides(fill="none")
```

## Nass

### Sockeye

Information on Alaskan exploitation of Nass sockeye comes primarily from the Northern Boundary Sockeye Run Reconstruction model, which uses estimated run-timing and migration route to provide estimates of interception rates in Alaska fisheries. We show timeseries of Alaskan exploitation rates for each Nass sockeye Conservation Unit with information (@fig-nass-trtc1) and the distribution of exploitation rates by CU (@fig-nass-trtc2).

```{r, fig-nass-trtc1,fig.height=5,fig.cap="Alaskan exploitation on Nass sockeye by CU."}
data<-fread("data-raw/sockeye-nass-trtc data.csv")

data$`AK ER`<-data$`Total ER`-data$`CDN ER`

ggplot(data,aes(x=Year,y=`AK ER`))+
  geom_point()+geom_line()+
  facet_wrap(CU_Name~.,ncol=3)+
  labs(y="Alaskan Exploitation Rate")+
  theme_bw()


```

```{r fig-nass-trtc2,fig.cap="Distribution of Alaskan exploitation rates on each Nass sockeye CU with information (1960-2023)."}
ggplot(data,aes(x=`AK ER`,y=reorder(CU_Name,`AK ER`,median),fill=CU_Name))+
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(height=.1)+
  labs(y="Conservation Unit",x="Alaskan Exploitation Rate")+
  theme_bw()+
  guides(fill="none")

```

## Transboundary

## Fraser

## Central Coast

## WCVI

## SOG
