---
title: "Alaskan Catch of BC Salmon"
output: html
execute:
  echo: false
  message: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
library(data.table)
library(tidyverse)

```

```{r source all scripts with functions}
source("R/skeena-sockeye-trtc-cu-akers.R")
source("R/nass-sockeye-trtc-cu-akers.R")

```

```{r read in all data needed}

skeena.sx.trtc<-fread("data-raw/sockeye-skeena-trtc data.csv")
nass.sx.trtc<-fread("data-raw/sockeye-nass-trtc data.csv")


```

# Southeast Alaska Catch Summary

# Southeast Alaska Catch of BC Salmon by Region

## Skeena

### Summary

-   Alaskan fisheries catch all species of salmon in the Skeena
-   Catch of Skeena sockeye is estimated through the Northern Boundary Run Reconstruction Model and can be very high in some years, especially on late timed populations

### Sockeye

#### Statistical Area


#### Conservation Units

Information on Alaskan exploitation of Skeena sockeye comes primarily from the Northern Boundary Sockeye Run Reconstruction model, which uses estimated run-timing and migration route to provide estimates of interception rates in Alaska fisheries. We show timeseries of Alaskan exploitation rates for each Skeena sockeye Conservation Unit with information (@fig-skeena-trtc1) and the distribution of exploitation rates (@fig-skeena-trtc2).

```{r fig-skeena-trtc1, fig.height=10,fig.cap="Alaskan exploitation rates for each Skeena sockeye Conservation Unit (1960-2023)."}

make.skeena.trtc.lineplot(skeena.sx.trtc)

```

```{r fig-skeena-trtc2,fig.height=8,fig.cap="Distribution of Alaskan exploitation rates on each Skeena sockeye CU with information (1960-2023)."}

make.skeena.trtc.boxplot(skeena.sx.trtc)

```

### Chinook




## Nass

### Sockeye

Information on Alaskan exploitation of Nass sockeye comes primarily from the Northern Boundary Sockeye Run Reconstruction model, which uses estimated run-timing and migration route to provide estimates of interception rates in Alaska fisheries. We show timeseries of Alaskan exploitation rates for each Nass sockeye Conservation Unit with information (@fig-nass-trtc1) and the distribution of exploitation rates by CU (@fig-nass-trtc2).

```{r fig-nass-trtc1,fig.height=5,fig.cap="Alaskan exploitation on Nass sockeye by CU."}

make.nass.trtc.lineplot(nass.sx.trtc)

```

```{r fig-nass-trtc2,fig.cap="Distribution of Alaskan exploitation rates on each Nass sockeye CU with information (1960-2023)."}

make.nass.trtc.boxplot(nass.sx.trtc)

```

## Transboundary

## Fraser

## Central Coast

## WCVI

## SOG

## Appendix 1: Pacific Salmon Commission Chinook Technical Committee Mortality Distribution Tables


